The Magnetorotational Instability Prefers Three Dimensions

### 2019-08-24 paper/paper.tex
small tweaks

Our results show that three-dimensional modes grow faster than two-dimensional modes whenever the MRI is near its critical shear values.
While we mainly focus on the ideal Keplerian case ($q=3/4$), we also demonstrate robustness for low Rossby ($q=1/10$) and Prandtl numbers ($\Prm=10^{-5}$).
There are several important future directions this work suggests.
First, the Sun possesses two internal shear layers with inwardly increasing shear, the high-latitude tachocline, and the near-surface shear layer (NSSL). Past work has already pointed out the possibility of the small-scale MRI in the Sun using local analysis \citep{doi:10.1086/522426,doi:10.1111/j.1745-3933.2010.00987.x,doi:10.1088/0004-637X/787/1/21}
The NSSL, in particular, may also host slower MRI-driven dynamics; in spite of containing small-scale convection.
It is therefore crucial to further elucidate the nonlinear saturation of the 3D MRI, along with its robustness to noisy convection.
Second, our low-$\Prm$ results suggest that three-dimensional MRI modes may be the easiest to excite in liquid metal experiments.
Determining possible non-axisymmetric signatures in Taylor-Couette experiments requires followup work using more realistic boundary conditions and geometry. 
Our prior work on the axisymmetric MRI \citep{2017ApJ...841....1C,2017ApJ...841....2C} shows only small differences between rotating plane- and cylindrical- Taylor-Couette geometries. 
We fully expect the general three-dimensional features of the MRI to persist in more complex applications.

>>>>

Our results show that three-dimensional modes grow faster than two-dimensional modes whenever the MRI is near its critical shear values.
While we mainly focus on the ideal Keplerian case ($q=3/4$), we also demonstrate robustness for low Rossby ($q=1/10$) and Prandtl numbers ($\Prm=10^{-5}$).
There are several important future directions this work suggests.
First, the Sun possesses two internal shear layers with inwardly increasing shear, the high-latitude tachocline, and the near-surface shear layer (NSSL). 
Past work has already pointed out the possibility of the small-scale MRI in the Sun using local analysis \citep{doi:10.1086/522426,doi:10.1111/j.1745-3933.2010.00987.x,doi:10.1088/0004-637X/787/1/21}.
The NSSL, in particular, may also host slower MRI-driven dynamics; in spite of containing small-scale convection.
It is therefore crucial to further elucidate the nonlinear saturation of the 3D MRI, along with its robustness to noisy convection.
Second, our low-$\Prm$ results suggest that three-dimensional MRI modes may be the easiest to excite in liquid metal experiments.
Determining possible non-axisymmetric signatures in Taylor-Couette experiments requires followup work using more realistic boundary conditions and geometry. 
Our prior work on the axisymmetric MRI \citep{2017ApJ...841....1C,2017ApJ...841....2C} shows only small differences between rotating plane- and cylindrical- Taylor-Couette geometries. 
We fully expect the general three-dimensional features of the MRI to persist in more complex applications.
